---
title: "Assignment 1"
---

My first assignment has three parts.

## (a) Brief Summary of Fireside Chats: Data Science and Industrial Engineering w/Cem Vardar [🧷](https://youtu.be/Fi8-phj1X1A)

(Sir I guess this might be a podcast title for your serie)

This talk started with an introduction to both Industrial Engineering and Data Science. Then, the conversation moved into the relationship between these two fields and explored specific sub-topics in data science. It gave a good description of what is specifically done in each area. After that, Cem Vardar shared his own professional experiences from his time at Carvana and informed us about tools we can learn on our own, like SQL, which would give us a competitive edge. Finally, he talked about the qualities a data scientist should have and gave us advice on the specific skills we need to focus on.

## (b) Question From The Talk

Q1: How does mastering Data Science benefit an Industrial Engineer?\
A1: As Mr. Vardar mentioned, we industrial engineers deal with complex problems. Data science is a powerful tool for solving these problems. Even knowing the basics gives us a holistic approach and the ability to see the system from the outside.

Q2: 1) Predictive Modelling

2)Machine Learning

3)Operations Research

According to the video, which of the above are directly related to data science?\
a) 1,2 b) 1,3 c) 2,3 d) 1,2,3

## (c) Tasks

```{r}
library(dslabs)
data("polls_us_election_2016")

my_first <- "Ece"        
my_birth_year <- 2003

#Define an integer k
k <- (nchar(my_first) + my_birth_year) %% 15 + 8

print(k)
```

```{r}
#Display k rows of the original data 
if (k %% 2 == 0) {
  print(head(polls_us_election_2016, k))
} else {
  print(tail(polls_us_election_2016, k))
}
```

```{r}
# the total number of NA values in the entire data set

total_na <- sum(is.na(polls_us_election_2016))
print(total_na)
```

```{r}
na_per_column <- sort(colSums(is.na(polls_us_election_2016)), decreasing = TRUE)
print(head(na_per_column, 8))
```

```{r}
# Get a new data
new_data <- polls_us_election_2016


for(i in 1:ncol(new_data)) {
  if(is.numeric(new_data[[i]])) {
    
    new_data[[i]][is.na(new_data[[i]])] <- my_birth_year + k
  } else {
    
    new_data[[i]] <- as.character(new_data[[i]])
    new_data[[i]][is.na(new_data[[i]])] <- paste0(my_first, "_", k)
  }
}

if (k %% 2 == 0) {
  print(head(new_data, k))
} else {
  print(tail(new_data, k))
}

print(paste("number of NA's in new data", sum(is.na(new_data))))

print(anyNA(new_data))
```

------------------------------------------------------------------------

### [**Note**]{.underline}

I struggled especially with the last past, tried to apply what I learned from the slides but still couldnt complete w/o getting help from AI.
